# Introduction {#intro}

This online book is a work-in-progress project and - thus - a living document. 

Here is a reference to ICAO Doc9854 [@icao_doc9854_2005].

It is also an end-of-year kick-off project ... and I need to see how this develops.
The principal idea is to create a useful resource for interested researcher and practitioner to analyse operational performance of air transportation / air navigation. 
This is done by providing wrapper functions for the tidyverse. 
How far I get with the package ... on vera :)

## Some example placeholders for cross-referencing

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(intro).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie_2015].
