--- 
title: "Operational ANS Performance with R/RStudio"
author: "Rainer Koelle"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rainer-rq-koelle/ansperfbook
description: "This is the initial version of the book Operational ANS Performance with R and RStudio. The book project aims at developing material for the harmonised application of the ICAO GANP key performance indicators based on the R-ecosystem. There is no project plan or deadline. Thus, you may find this version incomplete and are encouraged to come back to check for updates."
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

# Preface {-}

Operational performance analysis of air transportation and air navigation is essential to address the capabilities of local or regional systems, and the impact of capabilities or operational procedures.

Operational performance monitoring and reporting has become a higher visibility through the recent Global Air Navigation Plan (GANP). Through the GANP, International Civil Aviation Organisation (ICAO) links future ambitions with performance and stresses the need for local and regional performance monitoring.
Operational performance monitoring is well established in the US and Europe.
In the US, the Federal Aviation Authority (FAA), and in Europe, the Performance Review Unit (PRU), publish regular regional performance monitoring reports.
Both groups work together on a set of harmonised measures to compare the operational performance of the US and European air navigation system.

Expanding the scope of performance reporting and enable other parties to validate the results requires harmonised interpretation and implementation of the respective metrics.

To support benchmarking comparisons amongst different parties, the aim of this project is to develop an open-sourced based data analytical package ensuring the joint and harmonised application and implementation of performance metrics.

This book is an attempt of making use of R/RStudio and supporting packages (e.g. readr, dplyr) to harmonise the application of operational performance indicators.
As part of the R/RStudio universe, this book has been produced with the bookdown package.

The documentation is provided in the hope that it is useful to the reader.
Please report back about problems or queries you have relating to the use of the material presented or the corresponding R package.

The website for this (book) project is: https://rainer-rq-koelle.github.io/ansperfbook/.
The development website is: https://github.com/rainer-rq-koelle/ansperfbook.

The **ansperf** package is available at: https://github.com/rainer-rq-koelle/ansperf.

If you are interested in contributing to this development, please contact rainer.koelle@eurocontrol.int.     
You may also make use of the bookdown commenting feature which is based on Git. 
If you feel uncomfortable with doing so, please send an email.


<!--chapter:end:index.Rmd-->

# Front Matters {-}

## About this book {-}

This book documents a journey into using open source software for the operational performance analysis of Air Navigation Services.
The concepts presented in this book are informed by the experience of a series of international benchmarking projects. 
Discussions in - **and lessons learnt from** - these projects revolved around similar themes. This book would have not been possible without the discussions and generous time of all participants in these projects.

The book is written to help researchers, ANS performance analysts, and interested parties in establishing reproducible performance reports in accordance with the international conventions put together by the benchmarking community in response to the Key Performance Indicators proposed by ICAO in the on-going refinement of the Global Air Navigation Plan. 

## Structure of the book {-}

This book is organised in several parts.

```
to be developed
```

<!--chapter:end:00-frontmatters.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-literature.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-method.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-application.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-summary.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

